Explaining Amsterdam House Prices with Greenness

### 2023-04-11 README.Rmd
spelling mistake
update readme

---
title: "Explaining Noord-Holland house prices"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
date: "2023-03-21"

output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

@@

A Spatial Statistics and Spatial Machine Learning approach.

Below the structure, results, and some code of our research can be found.

@@

## We used the Funda-Scraper package to scrape our data

The query below was used to scrape our final research data on (28-03-2023).

```{python eval = FALSE}
scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False,\
n_pages = 1000)
df = scraper.run()
```
Note that this is not the original Funda-Scraper code underneath. The Function is adjusted to contain additional adress information, compared to the origional function. Code is included in the Scraper.ipynb file to copy the updated package into the site-packages directory of python.

## A pre-processing pipeline is used to enrich data

OSM was used to enrich the scraped data. We geocode adressess into geometries objects for in order to make use of the geospatial models.
Additional spatial data includes:

* Distance to public transport (Bus, Subway, and Train)
* Distance to public services (Schools, Universities, Shopping centres)

## This enriched data is used to fit an OLS model

### OLS on scraped data

```{r eval = FALSE}
model <- lm(price~ room + bedroom + bathroom + living_area + house_age, data = funda_data)
```

### OLS on enriched data

```{r eval = FALSE}
model <- lm(price~ room + bedroom + bathroom + living_area + house_age + bus_dist +subway_dist + train_dist + university_dist + school_dist + mall_dist + supermarket_dist, data = funda_data)
```

### GWR model to adjust for spatial component in the data

To look at local spatial dependence, a GWR model was fit on the data.

```{python eval = FALSE}
#Run basic GWR in parallel mode

gwr_selector = Sel_BW(b_coords, b_y, b_X)
gwr_bw = gwr_selector.search(pool = pool)
print(gwr_bw)
gwr_results = GWR(b_coords, b_y, b_X, gwr_bw).fit(pool = pool)

### MGWR model to adjust for spatial component in the data

As it would be more realistic to have different band-widths for every feature, MGWR was used

```{python eval = FALSE}
#run MGWR in parallel mode. Note: max_iter_multi needs to be specified

mgwr_selector = Sel_BW(b_coords, b_y, b_X, multi=True)
mgwr_bw = mgwr_selector.search(pool=pool, max_iter_multi=200, criterion = "AICc") 
print(mgwr_bw)
mgwr_results = MGWR(b_coords, b_y, b_X, selector=mgwr_selector).fit(pool=pool)

>>>>

---
title: "Explaining Amsterdam House Prices with Greenness"
subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"

output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)

@@

This study served as our term project performed at the end of the course Spatial Statistics and Machine Learning.

Below a short overview of the structure of the GitHub page, methodology, data sources, and code is provided.

Full paper can be found in the directory [here](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Paper/Term-Project---Grings%2C-Nauta%2C-Nibbering.pdf)!

@@

# Stucture of the directory
The way the data analysis was performed is described in the figure below. Below headers provide some insight into the steps that were taken during each phase.

![Overview of study area](Paper/figures/Methods.jpg)

## Data Extraction

The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in [the 1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).

The House price data was extracted with the help of the Funda-Scraper package. This code was however modified to be able to extract a more precise adress line, which could be used for geocoding the adress to spatial data.

The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced funda scraper in the site-packages or dist-packages directory of python:

```{python eval = F}
#import function to copy the scraper folder into the dist-packages or site-packages libraries
from copy_scraper import copy_scraper
copy_scraper()
```

To extract the data for this project, below query was used:

```{python eval = F}
####
# 2. Data
####
# Obtain Data
scraper = FundaScraper(area="amsterdam", want_to="buy", find_past=False, n_pages = 1000)
df = scraper.run()
```

Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb):

```{python eval = F}
####
# 1. Obtain Data
####
# Define Catalog
catalog = pystac_client.Client.open("https://planetarycomputer.microsoft.com/api/stac/v1",modifier=planetary_computer.sign_inplace)

# Obtain Area of Interest
bbox_of_interest = [4.541943,52.193249,5.212109,52.532048] 
time_of_interest = "2022-06-01/2022-09-30"

# Search Data
search = catalog.search(collections=["sentinel-2-l2a"],
                        bbox=bbox_of_interest,
                        datetime=time_of_interest,
                        query={"eo:cloud_cover": {"lt": 20}})

# Obtain Data
items = search.item_collection()

# Select Item from List
selected_item = items[4]

# Obtain Bands of Interest
data = odc.stac.stac_load([selected_item], bands = ['red', 'green', 'blue', 'nir'], bbox = bbox_of_interest).isel(time=0)
```

## Data Enhancement

To then use the data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column.

```{r eval = F}
df_geo <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4", "optional5"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4, optional5),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", addressline_city)) %>% 
  select(-optional1, -optional2, -optional3, -optional4, -optional5) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
```
